---
title: "Agricultural Analysis"
format: html
editor: visual
---

![]()

## Read in Data

```{r}
library(tidyverse)
library(sf)
library(here)
library(mapview)
library(RColorBrewer)
```

```{r}

ag_2015 <- st_read(here("data/Agricultural_Land_Use_2015_Baseline.geojson"))


```

```{r}

ag_2020 <- st_read(here("data/Agricultural_Land_Use_2020_Update.geojson"))

```

## Potential Questions

Histogram of acreage

crops by island

island map of color by crop

```{r}


```

## Make a Map

```{r}
mapview(ag_2015, zcol = "cropcatego")
```

### After looking at our mapview map, the map color scale 

## isn't that helpful to us... use r color brewer to change palette

```{r}



```

## Distribution of Acreage

```{r}
ggplot(ag_2015, aes(x = acreage)) +
  geom_histogram() +
  theme_bw() + 
  facet_wrap(~island, scales = "free_y")


```

Questions:

when you have 2 datasets what do you do... Compare them

Did we add crop acreage or lose crop acreage from 2015-2020?

```{r}

sum_2015_acreage <- sum(ag_2015$acreage)
sum_2020_acreage <- sum(ag_2020$acreage)

sum_2020_acreage - sum_2015_acreage 
```

Questions to ask from our loss from 2020-2015:

-   what has that land been converted to

\*We could make a map of lost ag land between 2015-2020

ag land ownership

NDVI in lost ag land

soil type
